The Name of the Title is Hope

### 2023-09-15 input/7_discussion.tex
Updates from Overleaf

\section{Discussion}
With this paper, we contributed a new way to design augmented experiences with the potential to maintain a user's SoA: a bleeding edge BCI to control EMS at moments of users' intention to interact. By leveraging an average of 11.5 EEG channels and using a simple, fast-to-compute feature, the BCI achieved a mean F1 score of .7. We demonstrated in eight participants that one effect of SoA, intentional binding, is maintained when using our INTENTION system. However, the subjectively rated level of control was lower when using the INTENTION system as compared to voluntary interaction without EMS. This was differentiated by participants' qualitative reports: when the stimulation aligned with participants' intentions, positive sentiments outweighed negative ones. When it did not, participants reported a negatively perceived loss of control.

% Sandwich: 
% Good -> [short] cool system, first of its kind setting out to augment user's action preceeding their movement in time
Our prototype was built using off-the-shelf, affordable, equipment to physically augment users' actions. Taken together, all the tech to control the users' movements, i.e., the EMS stimulation device, Arduino, and switchboard, cost less than 100 [anonymized]. While we used a 64-channel research-grade EEG system, the channel selection procedure resulted in the system ultimately using a low-density coverage of about 12 channels on average for classification. Today, many low-density EEG devices are available on consumer markets at affordable price points, see~\citet{Niso2023-ce} for a recent summary of available wireless systems.

Still, the system achieved what is considered to be a `good' F1 score of .7, and hence sometimes detected users' intention to interact. In our user study, this system performance affected users' performance in the time estimation task when comparing the three experimental conditions. We conclude that taking users' sentiments and ratings of control into account, this indicates a general modulation of agency with respect to augmentation. We believe this to be a very promising finding considering the fact that our prototype with low technological requirements still produces behavioral results indicating that intention can be detected and planned movements be augmented.

In line with the literature, we found that participants estimated the delay between tap and tone to be lower in both conditions where they were instructed to act on their own volition as compared to the passive condition~\cite{Moore2012-dk}. More recent literature has questioned the validity of the intentional binding phenomenon as a correlate of agency, stating that the effect may ``merely represent a strong case of multisensory causal binding.''~\cite{Suzuki2019-pi, Gutzeit2023-ei, Hoerl2020-my}. However, in our study, we observed the effect of compressing the action-outcome delay to be maintained even when using the INTENTION system. Hence, the effect was maintained for both conditions of voluntary action.

% Bad -> (1) situate the findings of the IB, (2) bad classification metrics not good enough to feel in control
\subsection{Limitations}
Two main procedural issues arose with respect to the time estimation task: First, contrasting INTENTION with BASELINE, we noted that when EMS moved participants' fingers, they sometimes reported that their finger was pressing on the touchscreen for a longer duration as compared to their `normal' touchscreen tap. This may have introduced additional variance in the time estimation task since the exact moment of the tap that causes the tone is more obscure. Second, following pilot recordings, we chose to obtain participants' time estimates by asking them to type in their estimates on the keyboard. However, we observed that many participants, while perceiving a continuous distribution of the delays, did not answer at a continuous ms resolution but rather at steps of 50 or 100ms, skewing the distribution of their answers. While many different versions of the intentional binding paradigm exist~\cite{Moore2012-dk}, we would now choose a continuous slider, perhaps set at different initial positions between trials, to obtain participants' estimates.

@@

For the current study, we must note the following limitations arising from the (potentially) insufficient performance of the classification system. To provide a full picture we first describe the impact from a signal detection point of view: False negative classifications meant that the system did not trigger an EMS pulse in line with participants intent to tap on the screen. On the other hand, false positive classification meant that an EMS pulse was sent in the absence of a true intention by the participant. Both cases, individually and jointly, had the potential to significantly impact the user experience and erode trust in the system. In the interviews, participants reported only a relatively low number of correctly detected intentions. This may have ultimately lead to a misalignment between users' perceptions and the observed, measurable, system behavior.

As a consequence, the insights gained into the INTENTION system's potential to preserve a sense of agency are, regrettably, limited. The quantitative metrics employed in our study, specifically those measuring the sense of control (including temporal binding and item assessment), may not have captured the nuanced temporal alignment experiences associated with EMS augmentation and user movement intentions but rather a more holistic assessment of the entire experimental block, which included trials with missed stimulation, too early stimulation, and some trials where the stimulation was in alignment with the participants' intent.

>>>>

\section{Discussion}
With this paper, we contributed a new way to design augmented experiences with the potential to maintain a user's SoA: a bleeding edge BCI to control EMS at moments of users' intention to interact. By leveraging an average of 11.5 EEG channels and using a simple, fast-to-compute feature, the BCI achieved a mean F1 score of .7. We demonstrated in eight participants that one effect of SoA, intentional binding, is maintained when using our system. However, the subjectively rated level of control was lower when using the system as compared to voluntary interaction without EMS. This was differentiated by participants' qualitative reports: when the stimulation aligned with participants' intentions, positive sentiments outweighed negative ones. When it did not, participants reported a negatively perceived loss of control.

% Sandwich: 
% Good -> [short] cool system, first of its kind setting out to augment user's action preceeding their movement in time
Our system was built using off-the-shelf, affordable, equipment to physically augment users' actions. Taken together, all the tech to control the users' movements, i.e., the EMS stimulation device, Arduino, and switchboard, cost less than 100 [anonymized]. While we used a 64-channel research-grade EEG system, the channel selection procedure resulted in the system ultimately using a low-density coverage of about 12 channels on average for classification. Today, many low-density EEG devices are available on consumer markets at affordable price points, see~\citet{Niso2023-ce} for a recent summary of available wireless systems.

Still, the system achieved what is considered to be a `good' F1 score of .7, and hence sometimes detected users' intention to interact. In our user study, this system performance affected users' performance in the time estimation task when comparing the three experimental conditions. We conclude that taking users' sentiments and ratings of control into account, this indicates a general modulation of agency with respect to intention-based augmentation. We believe this to be a very promising finding considering the fact that our prototype with low technological requirements still produces behavioral results indicating that intention can be detected and planned movements be augmented.

In line with the literature, we found that participants estimated the delay between tap and tone to be lower in both conditions where they were instructed to act on their own volition as compared to the passive condition~\cite{Moore2012-dk}. More recent literature has questioned the validity of the intentional binding phenomenon as a correlate of agency, stating that the effect may ``merely represent a strong case of multisensory causal binding.''~\cite{Suzuki2019-pi, Gutzeit2023-ei, Hoerl2020-my}. However, in our study, we observed the effect of compressing the action-outcome delay to be maintained even when using the system. Hence, the effect was maintained for both conditions of voluntary action.

% Bad -> (1) situate the findings of the IB, (2) bad classification metrics not good enough to feel in control
\subsection{Limitations}
Two main procedural issues arose with respect to the time estimation task: First, contrasting AUGMENTED with INTENTION, we noted that when EMS moved participants' fingers, they sometimes reported that their finger was pressing on the touchscreen for a longer duration as compared to their `normal' touchscreen tap. This may have introduced additional variance in the time estimation task since the exact moment of the tap that causes the tone is more obscure. Second, following pilot recordings, we chose to obtain participants' time estimates by asking them to type in their estimates on the keyboard. However, we observed that many participants, while perceiving a continuous distribution of the delays, did not answer at a continuous ms resolution but rather at steps of 50 or 100 ms, skewing the distribution of their answers. While many different versions of the intentional binding paradigm exist~\cite{Moore2012-dk}, we would now choose a continuous slider, perhaps set at different initial positions between trials, to obtain participants' estimates.

@@

For the current study, we must note the following limitations arising from the (potentially) insufficient performance of the classification system. To provide a full picture we first describe the impact from a signal detection point of view: False negative classifications meant that the system did not trigger an EMS pulse in line with participants intent to tap on the screen. On the other hand, false positive classification meant that an EMS pulse was sent in the absence of a true intention by the participant. Both cases, individually and jointly, had the potential to significantly impact the user experience and erode trust in the system. In the interviews, participants reported only a relatively low number of correctly detected intentions. This may have ultimately led to a misalignment between users' perceptions and the observed, measurable, system behavior.

As a consequence, the insights gained into the system's potential to preserve a sense of agency are, regrettably, limited. The quantitative metrics employed in our study, specifically those measuring the sense of control (including temporal binding and item assessment), may not have captured the nuanced temporal alignment experiences associated with EMS augmentation and user movement intentions but rather a more holistic assessment of the entire experimental block, which included trials with missed stimulation, too early stimulation, and some trials where the stimulation was in alignment with the participants' intent.
